---
title: "seaborn_ggplot学习手册"
author: "桑佳琪"
date: "2020年6月"
institute: 中南财经政法大学统计与数学学院
csl: ./style/chinese-gb7714-2015-numeric.csl
css: ./style/markdown.css
bibliography: [./Bibfile.bib]
eqnPrefixTemplate: ($$i$$)
link-citations: true
linkReferences: true
chapters: true
tableEqns: false
autoEqnLabels: false
classoption: "aspectratio=1610"
---

```{r setup, echo=F, purl=F}
knitr::opts_knit$set(root.dir = getwd())
knitr::opts_chunk$set(echo = TRUE, results = 'hide')
knitr::opts_chunk$set(warning = FALSE, message=FALSE)
knitr::opts_chunk$set(fig.align="center"
                      ## ,out.width="0.9\\textwidth" # latex
                      ,out.width="60%" # for both latex and html
                      ,fig.width=5, fig.height=3
                      )
```

```{r prepare, echo=F, purl=F}
rm(list=ls())
options(digits=4)
options(scipen=100)
graphics.off()
Sys.setlocale("LC_ALL", "Chinese")
library(reticulate)
```

**TODO**

- [x] seaborn
- [x] ggplot

# seaborn introduction
Seaborn is a library for making statistical graphics in Python. 
It is built on top of matplotlib and closely integrated with pandas data structures.

Here is some of the functionality that seaborn offers:
1.A dataset-oriented API for examining relationships between multiple variables

2.Specialized support for using categorical variables to show observations or aggregate statistics

3.Options for visualizing univariate or bivariate distributions and for comparing them between subsets of data

4.Automatic estimation and plotting of linear regression models for different kinds dependent variables

5.Convenient views onto the overall structure of complex datasets

6.High-level abstractions for structuring multi-plot grids that let you easily build complex visualizations

7.Concise control over matplotlib figure styling with several built-in themes

8.Tools for choosing color palettes that faithfully reveal patterns in your data

Seaborn aims to make visualization a central part of exploring and understanding data. Its dataset-oriented plotting functions operate on dataframes and arrays containing whole datasets and internally perform the necessary semantic mapping and statistical aggregation to produce informative plots.

```{python, results='markup'}


```

python图形

```{python}
import matplotlib.pyplot as plt
import seaborn as sns
from ggplot import *

```

# 使用说明

R输出表格

```{r, results='markup'}
knitr::kable(head(trees))
```

python 表格输出

```{python, results='markup'}
import pandas as pd
dat=pd.DataFrame([[1,2,3],[3,4,6]])
```


```{r eval=T, results='markup'}
knitr::kable(py$dat)
```

行内公式 $\alpha+\hat{\beta}$ 。

行间公式

$$\bar x = \sum_{i=1}^n x_i +\bar y$$

$$X \sim  N(0,1)$$


# 参考文献
[//]: # (\bibliography{Bibfile})
