---
title: "seaborn_ggplot学习手册"
author: "桑佳琪"
date: "2020年6月"
institute: 中南财经政法大学统计与数学学院
csl: ./style/chinese-gb7714-2015-numeric.csl
css: ./style/markdown.css
bibliography: [./Bibfile.bib]
eqnPrefixTemplate: ($$i$$)
link-citations: true
linkReferences: true
chapters: true
tableEqns: false
autoEqnLabels: false
classoption: "aspectratio=1610"
---

```{r setup, echo=F, purl=F}
knitr::opts_knit$set(root.dir = getwd())
knitr::opts_chunk$set(echo = TRUE, results = 'hide')
knitr::opts_chunk$set(warning = FALSE, message=FALSE)
knitr::opts_chunk$set(fig.align="center"
                      ## ,out.width="0.9\\textwidth" # latex
                      ,out.width="60%" # for both latex and html
                      ,fig.width=5, fig.height=3
                      )
```

```{r prepare, echo=F, purl=F}
rm(list=ls())
options(digits=4)
options(scipen=100)
graphics.off()
Sys.setlocale("LC_ALL", "Chinese")
library(reticulate)
```

**TODO**

- [x] seaborn
- [x] ggplot

# seaborn introduction

Seaborn is a library for making statistical graphics in Python. 
It is built on top of matplotlib and closely integrated with pandas data structures.

Here is some of the functionality that seaborn offers:
1.A dataset-oriented API for examining relationships between multiple variables

2.Specialized support for using categorical variables to show observations or aggregate statistics

3.Options for visualizing univariate or bivariate distributions and for comparing them between subsets of data

4.Automatic estimation and plotting of linear regression models for different kinds dependent variables

5.Convenient views onto the overall structure of complex datasets

6.High-level abstractions for structuring multi-plot grids that let you easily build complex visualizations

7.Concise control over matplotlib figure styling with several built-in themes

8.Tools for choosing color palettes that faithfully reveal patterns in your data

Seaborn aims to make visualization a central part of exploring and understanding data. Its dataset-oriented plotting functions operate on dataframes and arrays containing whole datasets and internally perform the necessary semantic mapping and statistical aggregation to produce informative plots.

## example

```{python}
import matplotlib.pyplot as plt
import pandas as pd
import seaborn as sns
sns.set()#默认主题
tips = pd.read_csv('./data/tips.csv')
sns.relplot(x="total_bill", y="tip", col="time",hue="smoker", style="smoker", size="size",data=tips)
```
```{python}
dots = pd.read_csv("./data/dots.csv")
sns.relplot(x="time", y="firing_rate", col="align",hue="choice", size="coherence", style="choice",facet_kws=dict(sharex=False),kind="line", legend="full", data=dots)
```

```{python}
fmri = sns.load_dataset("fmri") #统计误差
sns.relplot(x="timepoint", y="signal", col="region",
            hue="event", style="event",
            kind="line", data=fmri)
```

## lmplot 回归&点

```{python}
sns.lmplot(x="total_bill", y="tip", col="time", hue="smoker",data=tips)
```

## catplot

```{python}
sns.catplot(x="day", y="total_bill", hue="smoker",kind="swarm", data=tips)
```
```{python}
sns.catplot(x="day", y="total_bill", hue="smoker",kind="violin", split=True, data=tips)
```
```{python}
sns.catplot(x="day", y="total_bill", hue="smoker",kind="bar", data=tips)
```

## Figure-level and axes-level functions 多图

```{python}
import matplotlib.pyplot as plt#结合matplotlib
f, axes = plt.subplots(1, 2, sharey=True, figsize=(6, 4))
sns.boxplot(x="day", y="tip", data=tips, ax=axes[0])
sns.scatterplot(x="total_bill", y="tip", hue="day", data=tips, ax=axes[1])
```
```{python}
g = sns.catplot(x="total_bill", y="day", hue="time",height=3.5, aspect=1.5,kind="box", legend=False, data=tips);
g.add_legend(title="Meal")
g.set_axis_labels("Total bill ($)", "")
g.set(xlim=(0, 60), yticklabels=["Thursday", "Friday","Saturday", "Sunday"])
g.despine(trim=True)
g.fig.set_size_inches(6.5, 3.5)
g.ax.set_xticks([5, 15, 25, 35, 45, 55], minor=True)
plt.setp(g.ax.get_yticklabels(), rotation=30)
```
## jointplot 中间散点两边直方图

```{python}
iris = pd.read_csv("./data/iris.csv")
sns.jointplot(x="sepal_length", y="petal_length", data=iris)
```
```{python}
sns.pairplot(data=iris, hue="species")
```

## FacetGrid with custom projection 自定义投影？

```{python}
import numpy as np
import pandas as pd
import seaborn as sns
sns.set()
r = np.linspace(0, 10, num=100)
df = pd.DataFrame({'r': r, 'slow': r, 'medium': 2 * r, 'fast': 4 * r}) #设置原始数据
df = pd.melt(df, id_vars=['r'], var_name='speed', value_name='theta') #改变排列方式
g = sns.FacetGrid(df, col="speed", hue="speed",subplot_kws=dict(projection='polar'), height=4.5,sharex=False, sharey=False, despine=False)
g.map(sns.scatterplot, "theta", "r") #在画布上分布散点
```
```{python}
import numpy as np
import seaborn as sns
import matplotlib.pyplot as plt
sns.set(style="darkgrid")
g = sns.FacetGrid(tips, row="sex", col="time", margin_titles=True)
bins = np.linspace(0, 60, 13)
g.map(plt.hist, "total_bill", color="steelblue", bins=bins)```

## barplot 多行 (?)

```{python}
import numpy as np
import seaborn as sns
import matplotlib.pyplot as plt
sns.set(style="white", context="talk")
rs = np.random.RandomState(8)

# Set up the matplotlib figure
f, (ax1, ax2, ax3) = plt.subplots(3, 1, figsize=(7, 5), sharex=True)

# Generate some sequential data
x = np.array(list("ABCDEFGHIJ"))
y1 = np.arange(1, 11)
sns.barplot(x=x, y=y1, palette="rocket", ax=ax1)
ax1.axhline(0, color="k", clip_on=False)
ax1.set_ylabel("Sequential")

# Center the data to make it diverging
y2 = y1 - 5.5
sns.barplot(x=x, y=y2, palette="vlag", ax=ax2)
ax2.axhline(0, color="k", clip_on=False)
ax2.set_ylabel("Diverging")

# Randomly reorder the data to make it qualitative
y3 = rs.choice(y1, len(y1), replace=False)
sns.barplot(x=x, y=y3, palette="deep", ax=ax3)
ax3.axhline(0, color="k", clip_on=False)
ax3.set_ylabel("Qualitative")

# Finalize the plot
sns.despine(bottom=True)
plt.setp(f.axes, yticks=[])
plt.tight_layout(h_pad=2)
```

## heatmap(?) 热力图

```{python}
from string import ascii_letters
import numpy as np
import pandas as pd
import seaborn as sns
import matplotlib.pyplot as plt

sns.set(style="white")

# Generate a large random dataset
rs = np.random.RandomState(33)
d = pd.DataFrame(data=rs.normal(size=(100, 26)),columns=list(ascii_letters[26:]))

# Compute the correlation matrix
corr = d.corr()

# Generate a mask for the upper triangle
mask = np.triu(np.ones_like(corr, dtype=np.bool))

# Set up the matplotlib figure
f, ax = plt.subplots(figsize=(11, 9))

# Generate a custom diverging colormap
cmap = sns.diverging_palette(220, 10, as_cmap=True)

# Draw the heatmap with the mask and correct aspect ratio
sns.heatmap(corr, mask=mask, cmap=cmap, vmax=.3, center=0,square=True, linewidths=.5, cbar_kws={"shrink": .5})
```

## swarmplot(?)

```{python}
import pandas as pd
import seaborn as sns
sns.set(style="whitegrid", palette="muted")

# Load the example iris dataset
iris = pd.read_csv("./data/iris.csv")

# "Melt" the dataset to "long-form" or "tidy" representation
iris = pd.melt(iris, "species", var_name="measurement")

# Draw a categorical scatterplot to show each observation
sns.swarmplot(x="measurement", y="value", hue="species",palette=["r", "c", "y"], data=iris)
```

## clusterplot(?)

```{python}
import pandas as pd
import seaborn as sns
sns.set()

# Load the brain networks example dataset
df = pd.read_csv("./data/brain_networks.csv", header=[0, 1, 2], index_col=0)

# Select a subset of the networks
used_networks = [1, 5, 6, 7, 8, 12, 13, 17]
used_columns = (df.columns.get_level_values("network").astype(int).isin(used_networks))
df = df.loc[:, used_columns]

# Create a categorical palette to identify the networks
network_pal = sns.husl_palette(8, s=.45)
network_lut = dict(zip(map(str, used_networks), network_pal))

# Convert the palette to vectors that will be drawn on the side of the matrix
networks = df.columns.get_level_values("network")
network_colors = pd.Series(networks, index=df.columns).map(network_lut)

# Draw the full plot
sns.clustermap(df.corr(), center=0, cmap="vlag",row_colors=network_colors, col_colors=network_colors,linewidths=.75, figsize=(13, 13))
```
# ggplot 应用

## geom_abline用法

```{python}
from ggplot import *
import pandas as pd
# argument
#intercept	截距
#slope	斜率
#color  颜色
#size	宽度
mtcars=pd.read_csv("./data/mtcars.csv")
ggplot(mtcars,aes(x='wt',y='mpg')) + geom_point() +
geom_abline(intercept=37,slope=-5,colour="red",size=10)#颜色存在问题
```
## geom_now_its_art

```{python}
ggplot(mtcars, aes('wt', 'mpg')) + geom_point() +ggtitle("Not Art")
ggplot(mtcars, aes('wt', 'mpg')) + geom_now_its_art() +ggtitle("Art!")
# not useful but beautiful
```

## scale_color_brewer

```{python}
import numpy as np
import pandas as pd
from ggplot import *
import matplotlib.pyplot as plt
# type	颜色种类 Sequential (seq) | Qualitative (qual) | Diverging (div)
# palette 颜色组合 http://colorbrewer2.org/ for more details.

ggplot(aes(x='wt', y='hp'), data=mtcars) +geom_point() +scale_color_brewer(type='qual')
```

## theme

```
theme_bw
theme_gray
theme_matplotlib
theme_seaborn
theme_xkcd
```
## scale_color_gradient2

```{python, eval=F}
#low	Color for low end of gradient.
#high	Color for high end of gradient.
p = ggplot(aes(x='x', y='y', color='abs(x - y)'), data=dsub.head(1000)) +
geom_point() + scale_colour_gradient2(low="steelblue", high="black")

ggplot(aes(x='x', y='y', color='abs(x - y)'), data=dsub.head(1000)) +
geom_point() + scale_colour_gradient2(low="yellow", high="red")

# dsub数据集下载 颜色显示？
```


# 参考文献
[//]: # (\bibliography{Bibfile})
