---
title: "seaborn_ggplot学习手册"
author: "桑佳琪"
date: "2020年6月"
institute: 中南财经政法大学统计与数学学院
csl: ./style/chinese-gb7714-2015-numeric.csl
css: ./style/markdown.css
bibliography: [./Bibfile.bib]
eqnPrefixTemplate: ($$i$$)
link-citations: true
linkReferences: true
chapters: true
tableEqns: false
autoEqnLabels: false
classoption: "aspectratio=1610"
---

```{r setup, echo=F, purl=F}
knitr::opts_knit$set(root.dir = getwd())
knitr::opts_chunk$set(echo = TRUE, results = 'hide')
knitr::opts_chunk$set(warning = FALSE, message=FALSE)
knitr::opts_chunk$set(fig.align="center"
                      ## ,out.width="0.9\\textwidth" # latex
                      ,out.width="60%" # for both latex and html
                      ,fig.width=5, fig.height=3
                      )
```

```{r prepare, echo=F, purl=F}
rm(list=ls())
options(digits=4)
options(scipen=100)
graphics.off()
Sys.setlocale("LC_ALL", "Chinese")
library(reticulate)
```

**TODO**

- [x] seaborn
- [x] ggplot

# seaborn introduction
Seaborn is a library for making statistical graphics in Python. 
It is built on top of matplotlib and closely integrated with pandas data structures.

Here is some of the functionality that seaborn offers:
1.A dataset-oriented API for examining relationships between multiple variables

2.Specialized support for using categorical variables to show observations or aggregate statistics

3.Options for visualizing univariate or bivariate distributions and for comparing them between subsets of data

4.Automatic estimation and plotting of linear regression models for different kinds dependent variables

5.Convenient views onto the overall structure of complex datasets

6.High-level abstractions for structuring multi-plot grids that let you easily build complex visualizations

7.Concise control over matplotlib figure styling with several built-in themes

8.Tools for choosing color palettes that faithfully reveal patterns in your data

Seaborn aims to make visualization a central part of exploring and understanding data. Its dataset-oriented plotting functions operate on dataframes and arrays containing whole datasets and internally perform the necessary semantic mapping and statistical aggregation to produce informative plots.

```{python, results='markup'}


```


```{python}
import matplotlib.pyplot as plt
import seaborn as sns
from ggplot import *

```

```{python}

```
# ggplot 应用

## geom_abline用法

```{python}
from ggplot import *
import pandas as pd
# argument
#intercept	截距
#slope	斜率
#color  颜色
#size	宽度
mtcars=pd.read_csv("./data/mtcars.csv")
ggplot(mtcars,aes(x='wt',y='mpg')) + geom_point() +
geom_abline(intercept=37,slope=-5,colour="red",size=10)#颜色存在问题
```
## geom_now_its_art

```{python}
ggplot(mtcars, aes('wt', 'mpg')) + geom_point() +ggtitle("Not Art")
ggplot(mtcars, aes('wt', 'mpg')) + geom_now_its_art() +ggtitle("Art!")
# not useful but beautiful
```

## scale_color_brewer

```{python}
import numpy as np
import pandas as pd
from ggplot import *
import matplotlib.pyplot as plt
# type	颜色种类 Sequential (seq) | Qualitative (qual) | Diverging (div)
#palette 颜色组合 http://colorbrewer2.org/ for more details.

ggplot(aes(x='wt', y='hp'), data=mtcars) +geom_point() +scale_color_brewer(type='qual')
#diamonds数据集下载？
```

## theme

```
theme_bw
theme_gray
theme_matplotlib
theme_seaborn
theme_xkcd
```
## scale_color_gradient2

```{python, eval=F}
#low	Color for low end of gradient.
#high	Color for high end of gradient.
p = ggplot(aes(x='x', y='y', color='abs(x - y)'), data=dsub.head(1000)) +
geom_point() + scale_colour_gradient2(low="steelblue", high="black")

ggplot(aes(x='x', y='y', color='abs(x - y)'), data=dsub.head(1000)) +
geom_point() + scale_colour_gradient2(low="yellow", high="red")

# dsub数据集下载 颜色显示？
```


# 参考文献
[//]: # (\bibliography{Bibfile})
